---
title: "Intro to spatial analysis"
subtitle: ""
author: "Jakub Nowosad <br>nowosad.jakub@gmail.com"
date: "2017-04-26"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

## Introduction

---
class: inverse, center, middle
## Vector data

---
## The `sf` package

```{r, eval=FALSE}
devtools::install_github('edzer/sfr') # development version
install.packages('sf') # stable version
```

You need a recent version of the GDAL, GEOS, Proj.4, and UDUNITS libraries installed for this to work on Mac and Linux. More information of that at https://github.com/edzer/sfr.

```{r}
library('sf')
```

---
## Reading

```{r}
wrld <- st_read('data/wrld.shp')
```

```{r}
wrld <- st_read('data/wrld.gpkg')
```

---
## Writing

```{r, eval=FALSE}
st_write(wrld, 'data/wrld.shp')
```

```{r, eval=FALSE}
st_write(wrld, 'data/wrld.gpkg')
```

---
## `sf` structure

---
## CRS assignation

---
## Reprojection

---
## Attributes

---
## Simple map

---
class: inverse, center, middle
## Raster data

---
## Reading

---
## Writing

---
## `sf` structure

---
## CRS assignation

---
## Reprojection

---
## Attributes

---
## Simple map

---
class: inverse, center, middle
## Vector-Raster interactions

---
## Vector-Raster conversion

---
## Raster-Vector conversion

---
## Extract

---
## Crop

---
class: inverse, center, middle
## Advanced map-making

---
## tmap

---
## leaflet

---
class: inverse, center, middle
## Resources

---
## Resources


- [Documentation of the sf package](https://edzer.github.io/sfr/articles/sf1.html)
- [HOW-TO: Mapping in R just got a whole lot easier](http://www.computerworld.com/article/3175623/data-analytics/mapping-in-r-just-got-a-whole-lot-easier.html)
- [Spatial analysis in R with the sf package](https://cdn.rawgit.com/rhodyrstats/geospatial_with_sf/bc2b17cf/geospatial_with_sf.html)
- [Tidy spatial data in R: using dplyr, tidyr, and ggplot2 with sf](http://strimas.com/r/tidy-sf/)
- [Introduction to Working With Raster Data in R](http://neondataskills.org/tutorial-series/raster-data-series/)
- [Map and analyze raster data in R](http://zevross.com/blog/2015/03/30/map-and-analyze-raster-data-in-r/)
- [The Visual Raster Cheat Sheet](http://rpubs.com/etiennebr/visualraster)
- [Leaflet for R](http://rstudio.github.io/leaflet/)
- [Spatial Data Analysis and Modeling with R](http://rspatial.org/index.html)
- [Downloading and plotting MODIS Chlorophyll-a data](http://clarkrichards.org/r/oce/modis/chl/sp/raster/2017/03/25/modis-chl-data/)

- https://walkerke.github.io/tigris-webinar/#1
- https://github.com/walkerke/tigris

<!-- our book?? -->

